---
title: "Soil database creation"
author: "Amanda Pennino"
date: "4/22/2021"
output: html_document
---

```{r}
library(plyr)
library(tidyverse)
library(readxl)
```

Current database, create IDs
```{r}
DATA <- read_excel("data/raw/hb_pedons_analysis_0426.xlsx", sheet = "horizon data")
DATA$orig_ID <- paste(DATA$pedon, DATA$orig_horizon)
DATA$ID <- paste(DATA$pedon, DATA$horizon)
```

Combine subsampled horizons to give true thickness of each genetic horizon
```{r}
sum <- ddply(DATA, c("pedon", "orig_ID"), summarise,
      N = length(orig_ID),
      thick = sum(thick))

sub <- subset(DATA, is.na(DATA$subdivision) | DATA$subdivision == 1)

for(a in seq(1:nrow(sub))){
  if(isTRUE(sub$subdivision[a] == 1)){
    sub[a,7] <- sum[which(sum$orig_ID == sub$orig_ID[a]),4]
    sub[a,6] <- sub[a,5] + sub[a,7]
  }
}
```

then calculate HPU by excluding transitional horizons (is not AE, EA, EB, BE, BC, CB) and adding up any that contain "Bhs", "E", "Bh", "Bs"
this wont be necc for the auger one
new column "interface" that marks whether there is an R horizon or C... this might be different for the auger investigation
```{r}

```


if meets multiple conditions, concat two grades and mark "r" for review
```{r}

```

export
```{r}
out_dir <- "data/processed"

write_csv(DATA, paste(out_dir, "LATWAG_Soil_Database.csv", sep = "/"))

```

if you need to calculate averaged chemistry you can always use the sum data frame or calc and join

